Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-06-13 content.tex
Revised discussion

We showed how to use \verb;pirouette; to quantify the importance of a 
tree prior in Bayesian phylogenetics, using the simplest generative tree 
prior possible.
In principle any other (more complex) generative tree prior can be tested, 
but we chose to provide the simplest (and fastest to run) examples.
All examples used only one original tree,
where any speciation process produces a whole range of trees.
One tree is not enough to determine the impact of a tree prior 
on Bayesian inference.
However, if the same procedure were repeated and performed on a 
distribution with a sufficient number of generative trees, 
it would constitute a quantitative and effective assessment of the 
quality of the inference.
Also a twin tree does not always result in a lower error distribution,
due to the stochasticity in generating the twin tree.

In conclusion, \verb;pirouette; can directly show the comparison 
between the results obtained 
adopting a new generative prior as compared to the Bayesian inference error
when operating on a tree generated under a known and standard tree 
prior (the twin tree).
From such results an user can estimate whether or not a new tree prior, 
tailored on the generative process, is needed. 
If this were indeed the case, one could rightly implement 
their novel tree prior as an addition to 
their favorite Bayesian inference tool.

>>>>

We showed how to use \verb;pirouette; to quantify the importance of a 
tree prior in Bayesian phylogenetics, using the simplest generative tree 
prior possible.
In principle any other (more complex) generative tree prior can be tested, 
but we chose to provide the simplest (and fastest to run) examples.
All examples used only one original tree,
where any speciation process produces a whole range of trees.
One tree is not enough to determine the impact of a tree prior 
on Bayesian inference.
However, if the same procedure were repeated and performed on a 
distribution with a sufficient number of generative trees, 
it would constitute a quantitative and effective assessment of the 
quality of the inference.
Also a twin tree does not always result in a lower error distribution,
as the stochasticity in generating a twin tree will occasionally
yield a tree of very low likelihood.

In conclusion, \verb;pirouette; can show the errors
when adopting a new generative prior
in comparison to the errors made by a standard prior.
From such results an user can estimate whether or not a new tree prior, 
tailored on the generative process, is needed. 
If this were indeed the case, one could rightly implement 
their novel tree prior as an addition to 
their favorite Bayesian inference tool.
